Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-03 paper.tex
Abstract says 'canonical' instead of 'traditional'
Only tested on two machines so far

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes using hardware
acceleration have been developed, but they generally require a large amount of
geometry to be created every frame.  In the simple case where two axis-aligned
volumes intersect, it is shown that Boolean operations can be used so that
the camera may move without regenerating any geometry.  However, the two
variations presented herein still achieve similar frame rates to that of the
traditional slicing method.
\end{abstract}

@@

The performance of each approach was measured by using a simple frame counter
showing the number of frames rendered in the previous second.  Multiple camera
angles and scene configurations were tried in order to expose strong and weak
points of the approaches.  The tests were run on at least three different
machines with a variety of operating systems (Linux, Mac OS X) and video cards
(ATI, NVIDIA).  Table \ref{performance-table} shows the results.

>>>>

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes using hardware
acceleration have been developed, but they generally require a large amount of
geometry to be created every frame.  In the simple case where two axis-aligned
volumes intersect, it is shown that Boolean operations can be used so that
the camera may move without regenerating any geometry.  However, the two
variations presented herein still achieve similar frame rates to that of the
canonical slicing method.
\end{abstract}

@@

The performance of each approach was measured by using a simple frame counter
showing the number of frames rendered in the previous second.  Multiple camera
angles and scene configurations were tried in order to expose strong and weak
points of the approaches.  The tests were run on two different machines with a
variety of operating systems (Linux, Mac OS X) and video cards (ATI, NVIDIA).
Table \ref{performance-table} shows the results.
